### 2023-05-29 paper/Chapters/Chapter1.tex
Final updates

This paper has the following structure: in \cref{related_work}, we will describe
various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
In \cref{cha:background}, we will describe the key concepts of camera
calibration. Also, there we provide additional details on the underlying math,
for example, the derivation of the division model inversion. In
\cref{cha:approach}, we will describe the steps of the proposed method in
detail, including feature detection, initial camera calibration, camera
parameters estimation via minimization of the reprojection error, and the
process of searching and filtering the previously undetected features. In
\cref{Experiments}, we will describe the metrics we used, provide details about
the datasets, show the results of each of the algorithm's steps, and evaluate it
on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
results and outline future work.

>>>>

This paper has the following structure: in \cref{cha:related_work}, we will describe
various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
In \cref{cha:background}, we will describe the key concepts of camera
calibration. Also, there we provide additional details on the underlying math,
for example, the derivation of the division model inversion. In
\cref{cha:approach}, we will describe the steps of the proposed method in
detail, including feature detection, initial camera calibration, camera
parameters estimation via minimization of the reprojection error, and the
process of searching and filtering the previously undetected features. In
\cref{cha:experiments}, we will describe the metrics we used, provide details about
the datasets, show the results of each of the algorithm's steps, and evaluate it
on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
results and outline future work.

### 2023-05-29 paper/Chapters/Chapter4.tex
Final updates

For feature detection, we used the approach, proposed
by~\cite{geigerAutomaticCameraRange2012} (see \cref{sec:boards_features_detection,
	sec:classifier}).

@@

We chose to minimize the reprojection error between the board and back-projected
corners, which were initially detected. The projection and back-projection are
the inverse of each other, hence minimizing the error between the projection of
the board and the detected corners and minimizing the error between the
back-projection of the detected corners and the board are
equivalent\todo{Doesn't sound very rigorous to me.}. We minimized the error
between the board and the back-projected corners because back-projection does
not require the root finding.

>>>>

For feature detection, we used the approach, proposed
by~\cite{geigerAutomaticCameraRange2012} (see
\cref{sec:boards_features_detection,sec:classifier}).

@@

We chose to minimize the reprojection error between the board and back-projected
corners, which were initially detected. The projection and back-projection are
the inverse of each other, hence minimizing the error between the projection of
the board and the detected corners and minimizing the error between the
back-projection of the detected corners and the board are
equivalent. We minimized the error
between the board and the back-projected corners because back-projection does
not require the root finding.
